---
title: "Marketing Report"
subtitle: "Office of Marketing and Brand Management"
date: "`r Sys.Date()`"
output:
  pdf_document: default
---

```{r setup, include=FALSE}

library(knitr)
library(janitor)
library(tidyr)
library(zoo)
library(lubridate)
library(hms)
library(dplyr)
library(ggplot2)
library(gtable)
library(gridExtra)
library(grid)
library(ggpubr)
library(kableExtra)
library(scales)
library(hms)
library(stringr)
library(tinytex)

# invalidate cache when the tufte version changes
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE,
	cache.extra = packageVersion("tufte"),
	tidy = FALSE
	
)

```


```{r}
options(tinytex.verbose = TRUE)
```

# Findings

## LinkedIn

```{r}
Muskie <- read.csv("C:/Users/christine.iyer/Box/Agency Work Active Projects/Muskie/Data.csv", header = T, stringsAsFactors = F)
```

```{r fig.height=4, fig.width=8}

a <- dplyr::filter(Muskie, grepl('LI_WI', RunTime)) %>% dplyr::select(RunTime:POL)
d <- dplyr::filter(Muskie, grepl('LI_SP', RunTime)) %>% dplyr::select(RunTime:POL)
e <- dplyr::filter(Muskie, grepl('LI_FA', RunTime)) %>% dplyr::select(RunTime:POL)
f <- cbind.data.frame(a,d,e)

g <- f[, c(2:4, 7:8, 11:12 )]
kable(g, "latex", booktabs = T) %>% 
  kable_styling(full_width = T)%>%
  add_header_above(c(" " = 1, "LinkedIn Winter 2020" = 2, "LinkedIn Spring 2019" = 2, "LinkedIn Fall 20" = 2))
```

## Programmatic

```{r fig.height=4, fig.width=8}

a <- dplyr::filter(Muskie, grepl('DBM_WI', RunTime)) %>% dplyr::select(RunTime:POL)
d <- dplyr::filter(Muskie, grepl('DBM_SP', RunTime)) %>% dplyr::select(RunTime:POL)
e <- dplyr::filter(Muskie, grepl('DBM_FA', RunTime)) %>% dplyr::select(RunTime:POL)
f <- cbind.data.frame(a,d,e)

g <- f[, c(2:4, 7:8, 11:12 )]
kable(g, "latex", booktabs = T) %>% 
  kable_styling(full_width = T)%>%
  add_header_above(c(" " = 1, "Programmatic Winter 2020" = 2, "Programmatic Spring 2019" = 2, "Programmatic Fall 2019" = 2))
```


## Facebook

```{r fig.height=4, fig.width=8}

a <- dplyr::filter(Muskie, grepl('FB_WI', RunTime)) %>% dplyr::select(RunTime:POL)
d <- dplyr::filter(Muskie, grepl('FB_SP', RunTime)) %>% dplyr::select(RunTime:POL)
e <- dplyr::filter(Muskie, grepl('FB_FA', RunTime)) %>% dplyr::select(RunTime:POL)
f <- cbind.data.frame(a,d,e)

g <- f[, c(2:4, 7:8, 11:12 )]
kable(g, "latex", booktabs = T) %>% 
  kable_styling(full_width = T)%>%
  add_header_above(c(" " = 1, "Facebook Winter 2020" = 2, "Facebook Spring 2019" = 2, "Facebook Fall 2019" = 2))

  
```







# Conclusion

* We are pleased with LinkedIn and Doubleclick ad performance, the click-through-rates are above benchmark.

* Because of a "back to school" mindset in the Fall, we showed about 35% more Impressions. The 75% fewer unique pageviews in the Spring could be due to this viewer behavior. 

* The strong CTR from LinkedIn Sponsored content in the Fall is very encouraging and, despite a drop in the Spring , the metric remains well above benchmark. The percentage of web visits out of impressions shown remained consistent into the spring.

* Facebook CTR dropped from Fall to Spring. While we antipate lower values, it demands close consideration as it is below USM cutoff of 0.45%.


